Bayesian regression modelling facilitates quantitative modelling of cell metabolism

### 2023-10-27 paper/main.qmd
Update paper and supplementary information

---
title: "Hierarchical Bayesian regression modelling predicts biochemical rection energies and facilitates quantitative modelling of cell metabolism"
toc: true
abstract: >
  This paper presents Maud, a command-line application that implements
  Bayesian statistical inference for kinetic models of biochemical metabolic
  reaction networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Below, we
  review the existing options in this area, explain how Maud improves on the state
  of the art, describe the intended modelling workflow and illustrate its use with
  an example application.
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliation: DTU Biosustain
  - name: "Nicholas Luke Cowie"
    affiliation: DTU Biosustain
  - name: "Lars Keld Nielsen"
    affiliation: DTU Biosustain
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
  html:
   include-in-header: mathjax.html
  docx: default
---

>>>>

---
title: "Bayesian regression modelling facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism 
abstract: >
  This paper presents Maud, a command-line application that implements
  Bayesian statistical inference for kinetic models of biochemical metabolic
  reaction networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Below, we
  review the existing options in this area, explain how Maud improves on the state
  of the art, describe the intended modelling workflow and illustrate its use with
  an example application.
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
    - id: biosustain
      name: DTU Biosustain
  - name: "Nicholas Luke Cowie"
    affiliations: 
    - ref: biosustain
  - name: "Lars Keld Nielsen"
    affiliations: 
    - ref: biosustain
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
      abbreviations: IR,NMR,UV
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

### 2023-10-27 paper/main.tex
Update paper and supplementary information

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[journal=,manuscript=]{achemso}
\usepackage[version=3]{mhchem}
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

@@

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Hierarchical Bayesian regression modelling predicts biochemical rection energies and facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\title[]{Hierarchical Bayesian regression modelling predicts biochemical
rection energies and facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, breakable, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[journal=asbcd6,manuscript=article,layout=traditional]{achemso}
\usepackage[version=3]{mhchem}
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

@@

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Bayesian regression modelling facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  pdfkeywords={Bayesian inference, kinetic models of cell metabolism},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\keywords{Bayesian inference, kinetic models of cell metabolism}

\title[]{Bayesian regression modelling facilitates quantitative
modelling of cell metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}
